Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-22 robdml.tex
tex

\begin{figure}[t]
	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
	\caption{\oo{Performance plot with aligned conditions.
	(1) robustness and r1 under the same training cost;
	(2) r1 and training cost for reaching similar robustness;
	(3) training cost and robustness for reaching similar r1.}}
	\label{fig:introplot}
\end{figure}

>>>>

\begin{figure}[t]
	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
	\caption{
		%
		Comparison in robustness, training time cost, and recall@1 performance
		between our method and the state-of-the-art method.
		%
		Our method performs much better in all the three aspects.
		%
	}
	\label{fig:introplot}
\end{figure}
